---
title: "CRK cont SR - QAQC & plot"
author: "Moeka"
date: '2025-05-19'
output: github_document

---

```{r insatall packages}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

library(ggplot2)
library(dplyr)                  
library(tidyr)
library(googlesheets4)
library(lubridate)
library(PerformanceAnalytics)
library(ggpmisc)
library(Hmisc)
library(scales)
library(hms)
library(readxl)

# doesn't work anymore
#library(RespChamberProc)
## How to install RespChamberProc? -> Go to https://freesoft.dev/program/97026756.
```


Note: 
- 2022-08-16 ~ 2022-08-23: shallow/deep labels were not recorded. Have to be manually added. Port#5 = shallow; Port#14 = deep.
```{r read df}

setwd("G:/My Drive/Research/Projects/DC_auto/Data/SR")

# 2022-2024
# function - read and rbind the datasets
# importBind <- function(x){
#   temp <- list.files(pattern = paste0("*",x))
#   bind <- do.call("rbind", lapply(temp, read.csv, header = T))
#   return(bind)
# }

# read SoilFluxPro outputs in 2022-2024
# SR_cont_raw <- importBind("CRK_cont_SFP_qaqc")
# 
# SR_cont_raw <- read.csv("CRK_auto_SFP_qaqc_2022_2024.csv")

SR_cont_2022 <- read.csv("CRK_cont_SFP_qaqc_2022.csv") %>% mutate(Exp_R2 = as.double(Exp_R2))
SR_cont_2023 <- read.csv("CRK_cont_SFP_qaqc_2023.csv")
SR_cont_2024 <- 
  read.csv("CRK_cont_SFP_qaqc_2024.csv") %>% 
  mutate(across(Offset:Lin_R2, as.double)) %>% 
  mutate(across(Obs.:Port., as.double)) %>% 
  mutate(across(V1_IV:H2O_Mean, as.double))

SR_cont_raw <- rbind(SR_cont_2022, SR_cont_2023, SR_cont_2024)

str(SR_cont_raw)
unique(SR_cont_raw$Label)

# function to clean up the variables
clean_cont <- function(df){  
  df %>%
  mutate(Datetime_CST = as.POSIXct(Date_IV, format = "%m/%d/%Y %H:%M", tz = "Etc/GMT+6"),
         Flux = ifelse(grepl("Exp", CrvFitStatus), Exp_Flux, Lin_Flux),
         CV = ifelse(grepl("Exp", CrvFitStatus), Exp_FluxCV, Lin_FluxCV),
         R2 = ifelse(grepl("Exp", CrvFitStatus), as.numeric(Exp_R2), as.numeric(Lin_R2))) %>%
  filter(!is.na(Datetime_CST)) %>% 
  distinct()
  }

# clean up variables
SR_cont <- clean_cont(SR_cont_raw)

# clean up Label
SR_cont_v1 <- 
  SR_cont %>%
  mutate(Collar = case_when(Label == "shallow" ~ "sh1",
                            Label == "shallow2" ~ "sh2",
                            Label == "shallow3" ~ "sh3",
                            Label == "long" ~ "deep",
                            TRUE ~ Label)) %>%
  mutate(Collar = case_when(Collar == "" & Port. == "5" ~ "sh1",
                            Collar == "" & Port. == "14" ~ "deep",
                            TRUE ~ Collar))

# should be only 4 types
unique(SR_cont_v1$Collar)

summary(SR_cont_v1)
write.csv(SR_cont_v1, "CRK_cont_SFP_qaqc_2022_2024.csv", row.names = F)
```

"Obs.": doesn't matter much "Port.": Multiplexer port number (0 if not
using a multiplexer) "Date_IV": date type default is "M/DD/YYYY HH:SS"
"Offset": Offset (cm) used in volume calculation.

"CrvFitStatus": Curve fit solution. "Exp" means the exponential fit was
better than the linear fit (Exp_SSN \< Lin\_ SSN). "Lin" means the
linear fit was still better after the maximum number of iterations, and
the nonlinear coefficients have therefore been derived from linear fit.

"Exp_Flux": Flux computed from Exponential Fit. "Exp_FluxCV":
Coefficient of variance (%) of Exp Flux "Exp_R2": Correlation
coefficient for Exponential Fit. "Exp_Iter": Number of iterations used
in the Exponential Fit. "Lin_Flux": Flux computed from Linear Fit.
"Lin_FluxCV": Coefficient of variable (%) of Lin Flux "Lin_R2":
Correlation coefficient for the Linear Fit. "Observation.Length": The
original observation length. "V1_IV": Initial values of the voltage
channel\
"V1_Mean": Initial values of the voltage channel = Flow signals
"Cdry_Mean": Chamber CO2 concentration (μmol/mol), corrected for water
vapor dilution "Tcham_Mean": Air temperature (C) inside the soil chamber
during an active measurement (if no measurement is active, displays
Multiplexer case temperature)

"Pressure_Mean": Atmospheric pressure in the optical bench (kPa)
"H2O_Mean": Chamber water vapor concentration (mmol/mol) "Label": User
entered at time of data collection. "Vmux": Volume of the multiplexer
(if used) (cm3)

```{r raw data plot, fig.width=15,fig.height=8}

ggplot(SR_cont_v1) + 
  geom_point(aes(Datetime_CST, Flux, col = as.character(Collar))) + 
  theme_bw() 

```

```{r qaqc distribution, eval=FALSE}
knitr::opts_chunk$set(eval = FALSE)
# R2
ggplot(SR_cont_v1, aes(x = R2, col = Collar)) + 
  geom_freqpoly(bins = 100, size = .8, alpha = .5) + xlim(.96, 1) + theme_bw()

# CV
ggplot(SR_cont_v1, aes(x = CV, col = Collar)) + 
  geom_freqpoly(bins = 100, size = .8, alpha = .5) + xlim(.8, 2) + theme_bw()

# Cdry_Mean
ggplot(SR_cont_v1, aes(x = Cdry_IV, col = Collar)) + 
  geom_freqpoly(bins = 100, size = .8, alpha = .5) + xlim(350, 1000) + theme_bw()

# V1_Mean
ggplot(SR_cont_v1, aes(x = V1_IV, col = Collar)) + 
  geom_freqpoly(bins = 100, size = .8, alpha = .5) + theme_bw()


# V1 vs R2
ggplot(SR_cont_v1, aes(x = V1_IV, y = CV, col = as.character(Collar))) + 
  geom_point(size = .8, alpha = .5) + theme_bw() + ylim(.8, 10)
```


Try with R2 > .985, CV < 1.25, V1_IV > 2, Flux > 0

Deep collar installation 
- 1. 2022-04-29 
- 2. 2023-04-11 
- 3. 2023-10-29
- 4. 2024-06-15


```{r plot}
# boxplot after applying 3 variables
SR_cont_v1 %>% 
  filter(R2 > .985 & CV < 1.25 & V1_IV > 2 & Flux > 0) %>%
  ggplot() + 
  geom_boxplot(aes(as.character(Collar), Flux)) + 
  theme_bw()


# time series
SR_cont_v1 %>% 
  filter(R2 > .985 & CV < 1.25 & V1_IV > 2 & Flux > 0) %>% 
  ggplot() + 
  geom_point(aes(Datetime_CST, Flux, col = Collar)) +
  # deep collar insertion
  geom_vline(xintercept = as.POSIXct(c("2022-04-29", "2023-04-11", "2023-10-29", "2024-06-15")), 
             linetype = "dashed", color = "black") +
  theme_bw()



# suddenly got messier after 2023-08-27 19:00:00. Remove them
SR_cont_v1 %>% 
  filter((as.Date(Datetime_CST) > "2023-08-25") & as.Date(Datetime_CST) < "2023-09-20") %>% 
  ggplot() + geom_point(aes(Datetime_CST, Flux, col = Collar)) + 
  theme_classic()


```

# QAQC 
### Related to Flux
- R2 > 0.975
- CV < 1.9
- negative Flux

### Related to instrument
- V1_Mean > 2

### Bad data
- between 2023-08-25 and 2023-09-03
- sh3: by early 2024
- after the deep collar insertion in 6/15/2025
 (could be a different location)

## Expired/not ready deep collars
- June-July 2024
- after Nov 2024

Note: 
- Negative or very low flux can be captured by CV and V1 but not R2 as they can have clean lines
- V1 values depend on chambers but all of them should be over 2 when running properly
- Deep collar still observed very large fluxes which did not appear in other shallow collars even after QAQC with 3 variables above.



```{r qaqc data, fig.width=15,fig.height=8}
cont_qaqc <- 
  SR_cont_v1 %>% 
  filter(CV < 1.9 & R2 > 0.975 & V1_IV > 2 & Flux > 0) %>% 
  # bad data
  filter(!(Datetime_CST > "2023-08-27 19:00:00" & Datetime_CST < "2023-09-20")) %>% 
  # Remove bad sh3 data 
  filter(!(Collar == "sh3" & Datetime_CST > "2024-01-01 01:00:00" & Datetime_CST < "2024-06-05 00:00:00")) %>% 
  # Remove bad data after collar insertion in June 2024
  filter(!(Datetime_CST > "2024-06-14 01:00:00" & Datetime_CST < "2024-07-05 00:00:00")) %>% 
  # Remove expired deep data
  #filter(!(Collar == "deep" & Datetime_CST > "2022-06-15 01:00:00" & Datetime_CST < "2023-03-10 00:00:00")) %>% 
  # Remove too-early deep data
  filter(!(Collar == "deep" & Datetime_CST > "2024-06-13 01:00:00" & Datetime_CST < "2024-07-15 00:00:00")) %>% 
  # Remove expired deep data
  filter(!(Collar == "deep" & Datetime_CST > "2024-10-31 09:00:00")) %>% 
  arrange(Datetime_CST) %>% 
  select(Datetime_CST, Collar, Flux, CV, R2, V1_IV, Offset, Observation.Length, Cdry_Mean, Tcham_Mean, Pressure_Mean, H2O_Mean)

write.csv(cont_qaqc, "CRK_contSR_clean_2022_2024.csv", row.names = F)


# time series
cont_qaqc %>% 
  ggplot() + 
  geom_point(aes(Datetime_CST, Flux, col = Collar)) +
  # deep collar insertion
  geom_vline(xintercept = as.POSIXct(c("2022-04-29", "2023-04-11", "2023-10-29", "2024-06-15")), 
             linetype = "dashed", color = "black") +
  theme_bw()

```


```{r hourly}
cont_qaqc_hr <- 
  cont_qaqc %>%
  mutate(Datetime_hr_CST = floor_date(Datetime_CST, unit = "hour")) %>% # round it down
  select(Datetime_hr_CST, Flux, Collar) %>%
  pivot_wider(names_from = Collar,
              values_from = Flux,
              values_fn = ~ mean(.x, na.rm = TRUE)) %>% # when having duplicates
  rename(SR1 = sh1, SR2 = sh2, SR3 = sh3, Rh = deep) %>%
  mutate(Ra1 = SR1 - Rh, Ra2 = SR2 - Rh, Ra3 = SR3 - Rh) %>% 
  mutate(
    Year = year(Datetime_hr_CST),
    DoY = yday(Datetime_hr_CST),
    DoY_hr = DoY + (hour(Datetime_hr_CST))/24
    ) %>% 
  select(Year, DoY, DoY_hr, Datetime_hr_CST, SR1, SR2, SR3, Rh, Ra1, Ra2, Ra3)


write.csv(cont_qaqc_hr, "CRK_contSR_clean_hr_2022_2024.csv", row.names = F)
```




Term_1: 2022-05-22 and 2022-06-12: also available a few days around
2022-06-26

```{r when the pure Rh is available, fig.width=15,fig.height=8}
# data availability for 2022
cont_qaqc %>% 
  filter(format(as.Date(Datetime_CST),"%Y") == "2022") %>%
  ggplot() + 
  geom_point(aes(Datetime_CST, Flux, col = Collar), alpha = .5) + 
  theme_bw() + labs(color = "Collar type") + 
  ggtitle("Data avilable in 2022", subtitle = "Deep collar installed on Apr 29th") + 
  scale_x_datetime(date_breaks = "1 months", date_labels = "%b-%Y") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), axis.text.y = element_text(size = 15),
        legend.title = element_text(size = 15), legend.text = element_text(size = 15),
        plot.title = element_text(size = 15, face = "bold"))



# # deep available from 2022-05-22 11:25 am till 2022-06-09 15:25
# cont_qaqc %>% 
#   filter(Datetime_CST > "2022-05-22" & Datetime_CST < "2022-06-26") %>% 
#   ggplot() + geom_point(aes(Datetime_CST, Flux, col = Collar)) + theme_bw() +
#   ggtitle("1-2 months after deep collar installation", subtitle = "From 2022-05-22 to 2022-06-26")
# 
# 
# cont_qaqc %>% 
#   filter(Datetime_CST > "2022-11-22" & Datetime_CST < "2022-12-01") %>% 
#   ggplot() + geom_point(aes(Datetime_CST, Flux, col = as.character(Label))) + theme_bw() + 
#   ggtitle("7 months after deep collar installation", subtitle = "From 2022-11-23 to 2022-11-30")


# # data availability for 2023
cont_qaqc %>%
  filter(format(as.Date(Datetime_CST),"%Y") == "2023") %>%
  ggplot() +
  geom_point(aes(Datetime_CST, Flux, col = Collar), alpha = .5) +
  theme_bw() +  labs(color = "Collar type") +
  ggtitle("Data avilable in 2023", subtitle = "Deep collar installed on Apr 11th & Oct 29th") +
  scale_x_datetime(date_breaks = "2 months", date_labels = "%b-%Y") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), axis.text.y = element_text(size = 15),
        legend.title = element_text(size = 15), legend.text = element_text(size = 15),
        plot.title = element_text(size = 15, face = "bold"))
#  
# 
# cont_qaqc %>% 
#   filter(Datetime_CST < "2023-04-04" & Datetime_CST > "2023-03-10") %>% 
#   ggplot() + geom_point(aes(Datetime_CST, Flux, col = as.character(Label))) + theme_bw() + 
#   ggtitle("10-11 months after deep collar installation", subtitle = "From 2023-03-10 to 2023-04-04")


# REMOVE OUTLIERS >10
# cont_qaqc %>% 
#   filter(Datetime_CST > as.Date("2023-04-25") & Datetime_CST < as.Date("2023-06-08")) %>% 
#   ggplot() + geom_point(aes(Datetime_CST, Flux, col = as.character(Label))) + theme_bw()+ 
#   ggtitle("0-2 month after deep collar installation", subtitle = "From 2023-04-30 to 2023-06-08")
# 
# cont_qaqc %>% 
#   filter(Datetime_CST > as.Date("2023-05-23") & Datetime_CST < as.Date("2023-06-08")) %>% 
#   ggplot() + geom_point(aes(Datetime_CST, Flux, col = as.character(Label))) + theme_bw()+ 
#   ggtitle("0-2 month after deep collar installation", subtitle = "From 2023-05-20 to 2023-06-08")


# looking weird since end of august 2023
# cont_qaqc %>% 
#   filter(Datetime_CST < as.Date("2023-09-17") & Datetime_CST > as.Date("2023-08-10")) %>% 
#   filter(Flux < 10) %>% # did not get removed by filters
#   ggplot() + geom_point(aes(Datetime_CST, Flux, col = as.character(Label))) + theme_bw() + 
#   ggtitle("4-5 month after deep collar installation", subtitle = "From 2023-08-10 to 2023-09-17")


# # data availability for 2024
cont_qaqc %>% 
  filter(format(as.Date(Datetime_CST),"%Y") == "2024") %>%
  ggplot() + 
  geom_point(aes(Datetime_CST, Flux, col = Collar), alpha = .5) + 
  theme_bw() +  labs(color = "Collar type") + 
  ggtitle("Data avilable in 2024", subtitle = "Deep collar installed on Oct 29th, 2023") + 
  scale_x_datetime(date_labels = "%b-%Y") +
  theme(axis.title.x = element_blank(), axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 15), axis.text.y = element_text(size = 15),
        legend.title = element_text(size = 15), legend.text = element_text(size = 15),
        plot.title = element_text(size = 15, face = "bold"))

# cont_qaqc %>% 
#   filter(Datetime_CST > as.Date("2024-01-24") & Datetime_CST < as.Date("2024-02-05")) %>%# filter(Label %in% c("sh2", "deep")) %>%
#   ggplot() + geom_point(aes(Datetime_CST, Flux, col = as.character(Label)), alpha = .5) + theme_bw() + 
#   ggtitle("3 months after deep collar installation", subtitle = "From 2024-01-24 to 2024-02-05")


```



