---
title: "wavelet angle test"
author: "Moeka"
date: "2024-07-04"
output: github_document
---
wavelet analysis: chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/http://www.hs-stat.com/projects/WaveletComp/WaveletComp_guided_tour.pdf

- would it be better after deciding the period when thinking about the range??
- Normalization
All time series should be normalized to have zero mean and unit variance prior to wavelet analysis.  

- Gaps
Missing values in all the variables should be padded with zeros.

- results files are at DC_auto > Data > result_pad_64d_res

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(WaveletComp)
library(lubridate)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(tidyr)
library(broom)
library(forestmangr)
library(gridExtra)
library(purrr)
```


```{r read df}
setwd("G:/My Drive/Research/Projects/DC_auto/Data/GPP_SR_combined")

GPP_SR_MJ22 <- read.csv("GPP_SR_MJ22.csv") %>% mutate(date = as.POSIXct(Datetime_hr_CST, tz = "Etc/GMT+6"))
GPP_SR_MA23 <- read.csv("GPP_SR_MA23.csv") %>% mutate(date = as.POSIXct(Datetime_hr_CST, tz = "Etc/GMT+6"))
GPP_SR_Mar24 <- read.csv("GPP_SR_Mar24.csv") %>% mutate(date = as.POSIXct(Datetime_hr_CST, tz = "Etc/GMT+6"))
GPP_SR_Apr24 <- read.csv("GPP_SR_Apr24.csv") %>% mutate(date = as.POSIXct(Datetime_hr_CST, tz = "Etc/GMT+6"))
GPP_SR_Sep24 <- read.csv("GPP_SR_Sep24.csv") %>% mutate(date = as.POSIXct(Datetime_hr_CST, tz = "Etc/GMT+6"))
GPP_SR_Oct24 <- read.csv("GPP_SR_Oct24.csv") %>% mutate(date = as.POSIXct(Datetime_hr_CST, tz = "Etc/GMT+6"))
```

```{r daily Q10 function}

# function to calculate daily q10 and base respiration at 20 C
daily_q10 <- function(df, SR_col, Rh_col, Ra_col){
  
  df1 <- df %>%
    mutate(day = lubridate::date(date)) %>%
    rename("SR" = !!sym(SR_col)) %>%
    rename("Rh" = !!sym(Rh_col)) %>%
    rename("Ra" = !!sym(Ra_col)) 

  
  # for SR
  df_SR <- 
    df1 %>%
    nls_table(
      SR ~ R20 * Q10^((TS_1_1_1 - 20) / (10)),
      mod_start = c(R20 = 4, Q10 = 2),
      .groups = "day") %>%
    as.data.frame() %>%
    rename("SR20" = "b0", "Q10_SR" = "b1")
  
  df_Rh <- 
    df1 %>%
    nls_table(
      Rh ~ R20 * Q10^((TS_1_1_1 - 20) / (10)),
      mod_start = c(R20 = 4, Q10 = 2),
      .groups = "day") %>%
    as.data.frame() %>%
    rename("Rh20" = "b0", "Q10_Rh" = "b1")
  
  df_Ra <- 
    df1 %>%
    nls_table(
      Ra ~ R20 * Q10^((TS_1_1_1 - 20) / (10)),
      mod_start = c(R20 = 4, Q10 = 2),
      .groups = "day") %>%
    as.data.frame() %>%
    rename("Ra20" = "b0", "Q10_Ra" = "b1")
    
  
  df2 <- 
    list(df_SR, df_Rh, df_Ra) %>% 
    reduce(full_join, by = 'day') 
  
  output <- 
    left_join(df1, df2, by = "day") %>%
    mutate(rSR = SR - SR20,
           rRh = Rh - Rh20,
           rRa = Ra - Ra20)
    
  
  return(output)
}

```

Run the (co)spectral function in 02 first. Will use the same function below.

```{r location to save}
# hourly data with dialy Q10
dir_res1_pwr = "G:/My Drive/Research/Projects/DC_auto/Data/Result/GPP_SR_cospectral/res_64d_one_GPP_hourly_dailyQ10/df_temporal_pwr/"
dir_res1_diurnal = "G:/My Drive/Research/Projects/DC_auto/Data/Result/GPP_SR_cospectral/res_64d_one_GPP_hourly_dailyQ10/df_diurnal/"
dir_res1_df = "G:/My Drive/Research/Projects/DC_auto/Data/Result/GPP_SR_cospectral/res_64d_one_GPP_hourly_dailyQ10/df/"
```

```{r CWT 2022}
# take residuals
GPP_SR_MJ22_res1 <- daily_q10(GPP_SR_MJ22, "SR1", "Rh", "Ra1")
write.csv(GPP_SR_MJ22_res1, paste0(dir_res1_df, "MJ22.csv"), row.names = F)

# residual Rh
wc_rRh_MJ22 <- wc_summary(GPP_SR_MJ22_res1, "rRh")

# heatmap
wc_img_gen(wc_rRh_MJ22, "rRh")

# temporal power data & graph
rRh_GPP_MJ22_pwr <- wc_avg(wc_rRh_MJ22$GPP, 25)
rRh_PAR_MJ22_pwr <- wc_avg(wc_rRh_MJ22$PAR, 25)
rRh_Ts_MJ22_pwr <- wc_avg(wc_rRh_MJ22$Ts, 25)
rRh_VWC_MJ22_pwr <- wc_avg(wc_rRh_MJ22$VWC, 25)

# csv output
write.csv(rRh_GPP_MJ22_pwr$df, paste0(dir_res1_pwr, "rRh_GPP_MJ22.csv"), row.names = F)
write.csv(rRh_PAR_MJ22_pwr$df, paste0(dir_res1_pwr, "rRh_PAR_MJ22.csv"), row.names = F)
write.csv(rRh_Ts_MJ22_pwr$df, paste0(dir_res1_pwr, "rRh_Ts_MJ22.csv"), row.names = F)
write.csv(rRh_VWC_MJ22_pwr$df, paste0(dir_res1_pwr, "rRh_VWC_MJ22.csv"), row.names = F)


# extracting diurnal angle & power patterns from heatmap
wc_rRh_MJ22_diurnal_summary <- wc_result_summary(GPP_SR_MJ22_res1, "rRh", wc_rRh_MJ22)
save_to_csv(wc_rRh_MJ22_diurnal_summary, dir_res1_diurnal, "wc_rRh_MJ22_")


# viz
ggarrange(
  wc_lag_img(wc_rRh_MJ22_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRh_MJ22_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_MJ22_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_MJ22_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)


# residual Ra
wc_rRa_MJ22 <- wc_summary(GPP_SR_MJ22_res1, "rRa")

# heatmap
wc_img_gen(wc_rRa_MJ22, "rRa")

# temporal power data & graph
rRa_GPP_MJ22_pwr <- wc_avg(wc_rRa_MJ22$GPP, 25)
rRa_PAR_MJ22_pwr <- wc_avg(wc_rRa_MJ22$PAR, 25)
rRa_Ts_MJ22_pwr <- wc_avg(wc_rRa_MJ22$Ts, 25)
rRa_VWC_MJ22_pwr <- wc_avg(wc_rRa_MJ22$VWC, 25)

# csv output
write.csv(rRa_GPP_MJ22_pwr$df, paste0(dir_res1_pwr, "rRa_GPP_MJ22.csv"), row.names = F)
write.csv(rRa_PAR_MJ22_pwr$df, paste0(dir_res1_pwr, "rRa_PAR_MJ22.csv"), row.names = F)
write.csv(rRa_Ts_MJ22_pwr$df, paste0(dir_res1_pwr, "rRa_Ts_MJ22.csv"), row.names = F)
write.csv(rRa_VWC_MJ22_pwr$df, paste0(dir_res1_pwr, "rRa_VWC_MJ22.csv"), row.names = F)


# extracting diurnal angle & power patterns from heatmap
wc_rRa_MJ22_diurnal_summary <- wc_result_summary(GPP_SR_MJ22_res1, "rRa", wc_rRa_MJ22)
save_to_csv(wc_rRa_MJ22_diurnal_summary, dir_res1_diurnal, "wc_rRa_MJ22_")


# viz
ggarrange(
  wc_lag_img(wc_rRa_MJ22_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRa_MJ22_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_MJ22_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_MJ22_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)

```

```{r WT 2022}
wt_rRh_MJ22 <- 
  analyze.wavelet(wc_rRh_MJ22$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_MJ22_pwr <- wt_avg(wt_rRh_MJ22, 25)
write.csv(rRh_MJ22_pwr$df, paste0(dir_res1_pwr, "rRh_MJ22.csv"), row.names = F)

wt.image(wt_rRh_MJ22,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRh"
)

# rRa
wt_rRa_MJ22 <- 
  analyze.wavelet(wc_rRa_MJ22$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_MJ22_pwr <- wt_avg(wt_rRa_MJ22, 25)
write.csv(rRa_MJ22_pwr$df, paste0(dir_res1_pwr, "rRa_MJ22.csv"), row.names = F)

wt.image(wt_rRa_MJ22,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRa"
)
```

```{r CWT 2023}
# take residuals
GPP_SR_MA23_res1 <- daily_q10(GPP_SR_MA23, "SR1", "Rh", "Ra1")
write.csv(GPP_SR_MA23_res1, paste0(dir_res1_df, "MA23.csv"), row.names = F)

# residual Rh
wc_rRh_MA23 <- wc_summary(GPP_SR_MA23_res1, "rRh")

# heatmap
wc_img_gen(wc_rRh_MA23, "rRh")

# temporal power data & graph
rRh_GPP_MA23_pwr <- wc_avg(wc_rRh_MA23$GPP, 25)
rRh_PAR_MA23_pwr <- wc_avg(wc_rRh_MA23$PAR, 25)
rRh_Ts_MA23_pwr <- wc_avg(wc_rRh_MA23$Ts, 25)
rRh_VWC_MA23_pwr <- wc_avg(wc_rRh_MA23$VWC, 25)

# csv output
write.csv(rRh_GPP_MA23_pwr$df, paste0(dir_res1_pwr, "rRh_GPP_MA23.csv"), row.names = F)
write.csv(rRh_PAR_MA23_pwr$df, paste0(dir_res1_pwr, "rRh_PAR_MA23.csv"), row.names = F)
write.csv(rRh_Ts_MA23_pwr$df, paste0(dir_res1_pwr, "rRh_Ts_MA23.csv"), row.names = F)
write.csv(rRh_VWC_MA23_pwr$df, paste0(dir_res1_pwr, "rRh_VWC_MA23.csv"), row.names = F)

# extracting diurnal angle & power patterns from heatmap
wc_rRh_MA23_diurnal_summary <- wc_result_summary(GPP_SR_MA23_res1, "rRh", wc_rRh_MA23)
save_to_csv(wc_rRh_MA23_diurnal_summary, dir_res1_diurnal, "wc_rRh_MA23_")

# viz
ggarrange(
  wc_lag_img(wc_rRh_MA23_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRh_MA23_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_MA23_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_MA23_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)


# residual Ra
wc_rRa_MA23 <- wc_summary(GPP_SR_MA23_res1, "rRa")

# heatmap
wc_img_gen(wc_rRa_MA23, "rRa")

# temporal power data & graph
rRa_GPP_MA23_pwr <- wc_avg(wc_rRa_MA23$GPP, 25)
rRa_PAR_MA23_pwr <- wc_avg(wc_rRa_MA23$PAR, 25)
rRa_Ts_MA23_pwr <- wc_avg(wc_rRa_MA23$Ts, 25)
rRa_VWC_MA23_pwr <- wc_avg(wc_rRa_MA23$VWC, 25)

# csv output
write.csv(rRa_GPP_MA23_pwr$df, paste0(dir_res1_pwr, "rRa_GPP_MA23.csv"), row.names = F)
write.csv(rRa_PAR_MA23_pwr$df, paste0(dir_res1_pwr, "rRa_PAR_MA23.csv"), row.names = F)
write.csv(rRa_Ts_MA23_pwr$df, paste0(dir_res1_pwr, "rRa_Ts_MA23.csv"), row.names = F)
write.csv(rRa_VWC_MA23_pwr$df, paste0(dir_res1_pwr, "rRa_VWC_MA23.csv"), row.names = F)


# extracting diurnal angle & power patterns from heatmap
wc_rRa_MA23_diurnal_summary <- wc_result_summary(GPP_SR_MA23_res1, "rRa", wc_rRa_MA23)
save_to_csv(wc_rRa_MA23_diurnal_summary, dir_res1_diurnal, "wc_rRa_MA23_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_MA23_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRa_MA23_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_MA23_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_MA23_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)

```

```{r WT 2023}
wt_rRh_MA23 <- 
  analyze.wavelet(wc_rRh_MA23$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_MA23_pwr <- wt_avg(wt_rRh_MA23, 25)
write.csv(rRh_MA23_pwr$df, paste0(dir_res1_pwr, "rRh_MA23.csv"), row.names = F)

wt.image(wt_rRh_MA23,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRh"
)

# rRa
wt_rRa_MA23 <- 
  analyze.wavelet(wc_rRa_MA23$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_MA23_pwr <- wt_avg(wt_rRa_MA23, 25)
write.csv(rRa_MA23_pwr$df, paste0(dir_res1_pwr, "rRa_MA23.csv"), row.names = F)

wt.image(wt_rRa_MA23,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRa"
)
```

```{r CWT Mar24}
# take residuals
GPP_SR_Mar24_res1 <- daily_q10(GPP_SR_Mar24, "SR", "Rh", "Ra")
write.csv(GPP_SR_Mar24_res1, paste0(dir_res1_df, "Mar24.csv"), row.names = F)

# residual Rh
wc_rRh_Mar24 <- wc_summary(GPP_SR_Mar24_res1, "rRh")

# heatmap
wc_img_gen(wc_rRh_Mar24, "rRh")

# temporal power data & graph
rRh_GPP_Mar24_pwr <- wc_avg(wc_rRh_Mar24$GPP, 25)
rRh_PAR_Mar24_pwr <- wc_avg(wc_rRh_Mar24$PAR, 25)
rRh_Ts_Mar24_pwr <- wc_avg(wc_rRh_Mar24$Ts, 25)
rRh_VWC_Mar24_pwr <- wc_avg(wc_rRh_Mar24$VWC, 25)

# csv output
write.csv(rRh_GPP_Mar24_pwr$df, paste0(dir_res1_pwr, "rRh_GPP_Mar24.csv"), row.names = F)
write.csv(rRh_PAR_Mar24_pwr$df, paste0(dir_res1_pwr, "rRh_PAR_Mar24.csv"), row.names = F)
write.csv(rRh_Ts_Mar24_pwr$df, paste0(dir_res1_pwr, "rRh_Ts_Mar24.csv"), row.names = F)
write.csv(rRh_VWC_Mar24_pwr$df, paste0(dir_res1_pwr, "rRh_VWC_Mar24.csv"), row.names = F)

# extracting diurnal angle & power patterns from heatmap
wc_rRh_Mar24_diurnal_summary <- wc_result_summary(GPP_SR_Mar24_res1, "rRh", wc_rRh_Mar24)
save_to_csv(wc_rRh_Mar24_diurnal_summary, dir_res1_diurnal, "wc_rRh_Mar24_")

# viz
ggarrange(
  wc_lag_img(wc_rRh_Mar24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRh_Mar24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Mar24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Mar24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)


# residual Ra
wc_rRa_Mar24 <- wc_summary(GPP_SR_Mar24_res1, "rRa")

# heatmap
wc_img_gen(wc_rRa_Mar24, "rRa")

# temporal power data & graph
rRa_GPP_Mar24_pwr <- wc_avg(wc_rRa_Mar24$GPP, 25)
rRa_PAR_Mar24_pwr <- wc_avg(wc_rRa_Mar24$PAR, 25)
rRa_Ts_Mar24_pwr <- wc_avg(wc_rRa_Mar24$Ts, 25)
rRa_VWC_Mar24_pwr <- wc_avg(wc_rRa_Mar24$VWC, 25)

# csv output
write.csv(rRa_GPP_Mar24_pwr$df, paste0(dir_res1_pwr, "rRa_GPP_Mar24.csv"), row.names = F)
write.csv(rRa_PAR_Mar24_pwr$df, paste0(dir_res1_pwr, "rRa_PAR_Mar24.csv"), row.names = F)
write.csv(rRa_Ts_Mar24_pwr$df, paste0(dir_res1_pwr, "rRa_Ts_Mar24.csv"), row.names = F)
write.csv(rRa_VWC_Mar24_pwr$df, paste0(dir_res1_pwr, "rRa_VWC_Mar24.csv"), row.names = F)


# extracting diurnal angle & power patterns from heatmap
wc_rRa_Mar24_diurnal_summary <- wc_result_summary(GPP_SR_Mar24_res1, "rRa", wc_rRa_Mar24)
save_to_csv(wc_rRa_Mar24_diurnal_summary, dir_res1_diurnal, "wc_rRa_Mar24_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_Mar24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRa_Mar24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Mar24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Mar24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)

```

```{r WT Mar24}
wt_rRh_Mar24 <- 
  analyze.wavelet(wc_rRh_Mar24$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_Mar24_pwr <- wt_avg(wt_rRh_Mar24, 25)
write.csv(rRh_Mar24_pwr$df, paste0(dir_res1_pwr, "rRh_Mar24.csv"), row.names = F)

wt.image(wt_rRh_Mar24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRh"
)

# rRa
wt_rRa_Mar24 <- 
  analyze.wavelet(wc_rRa_Mar24$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_Mar24_pwr <- wt_avg(wt_rRa_Mar24, 25)
write.csv(rRa_Mar24_pwr$df, paste0(dir_res1_pwr, "rRa_Mar24.csv"), row.names = F)

wt.image(wt_rRa_Mar24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRa"
)
```

```{r CWT Apr24}
# take residuals
GPP_SR_Apr24_res1 <- daily_q10(GPP_SR_Apr24, "SR", "Rh", "Ra")
write.csv(GPP_SR_Apr24_res1, paste0(dir_res1_df, "Apr24.csv"), row.names = F)

# residual Rh
wc_rRh_Apr24 <- wc_summary(GPP_SR_Apr24_res1, "rRh")

# heatmap
wc_img_gen(wc_rRh_Apr24, "rRh")

# temporal power data & graph
rRh_GPP_Apr24_pwr <- wc_avg(wc_rRh_Apr24$GPP, 25)
rRh_PAR_Apr24_pwr <- wc_avg(wc_rRh_Apr24$PAR, 25)
rRh_Ts_Apr24_pwr <- wc_avg(wc_rRh_Apr24$Ts, 25)
rRh_VWC_Apr24_pwr <- wc_avg(wc_rRh_Apr24$VWC, 25)

# csv output
write.csv(rRh_GPP_Apr24_pwr$df, paste0(dir_res1_pwr, "rRh_GPP_Apr24.csv"), row.names = F)
write.csv(rRh_PAR_Apr24_pwr$df, paste0(dir_res1_pwr, "rRh_PAR_Apr24.csv"), row.names = F)
write.csv(rRh_Ts_Apr24_pwr$df, paste0(dir_res1_pwr, "rRh_Ts_Apr24.csv"), row.names = F)
write.csv(rRh_VWC_Apr24_pwr$df, paste0(dir_res1_pwr, "rRh_VWC_Apr24.csv"), row.names = F)

# extracting diurnal angle & power patterns from heatmap
wc_rRh_Apr24_diurnal_summary <- wc_result_summary(GPP_SR_Apr24_res1, "rRh", wc_rRh_Apr24)
save_to_csv(wc_rRh_Apr24_diurnal_summary, dir_res1_diurnal, "wc_rRh_Apr24_")

# viz
ggarrange(
  wc_lag_img(wc_rRh_Apr24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRh_Apr24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Apr24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Apr24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)


# residual Ra
wc_rRa_Apr24 <- wc_summary(GPP_SR_Apr24_res1, "rRa")

# heatmap
wc_img_gen(wc_rRa_Apr24, "rRa")

# temporal power data & graph
rRa_GPP_Apr24_pwr <- wc_avg(wc_rRa_Apr24$GPP, 25)
rRa_PAR_Apr24_pwr <- wc_avg(wc_rRa_Apr24$PAR, 25)
rRa_Ts_Apr24_pwr <- wc_avg(wc_rRa_Apr24$Ts, 25)
rRa_VWC_Apr24_pwr <- wc_avg(wc_rRa_Apr24$VWC, 25)

# csv output
write.csv(rRa_GPP_Apr24_pwr$df, paste0(dir_res1_pwr, "rRa_GPP_Apr24.csv"), row.names = F)
write.csv(rRa_PAR_Apr24_pwr$df, paste0(dir_res1_pwr, "rRa_PAR_Apr24.csv"), row.names = F)
write.csv(rRa_Ts_Apr24_pwr$df, paste0(dir_res1_pwr, "rRa_Ts_Apr24.csv"), row.names = F)
write.csv(rRa_VWC_Apr24_pwr$df, paste0(dir_res1_pwr, "rRa_VWC_Apr24.csv"), row.names = F)


# extracting diurnal angle & power patterns from heatmap
wc_rRa_Apr24_diurnal_summary <- wc_result_summary(GPP_SR_Apr24_res1, "rRa", wc_rRa_Apr24)
save_to_csv(wc_rRa_Apr24_diurnal_summary, dir_res1_diurnal, "wc_rRa_Apr24_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_Apr24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRa_Apr24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Apr24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Apr24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)

```

```{r WT Apr24}
wt_rRh_Apr24 <- 
  analyze.wavelet(wc_rRh_Apr24$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_Apr24_pwr <- wt_avg(wt_rRh_Apr24, 25)
write.csv(rRh_Apr24_pwr$df, paste0(dir_res1_pwr, "rRh_Apr24.csv"), row.names = F)

wt.image(wt_rRh_Apr24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRh"
)

# rRa
wt_rRa_Apr24 <- 
  analyze.wavelet(wc_rRa_Apr24$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_Apr24_pwr <- wt_avg(wt_rRa_Apr24, 25)
write.csv(rRa_Apr24_pwr$df, paste0(dir_res1_pwr, "rRa_Apr24.csv"), row.names = F)

wt.image(wt_rRa_Apr24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRa"
)
```

```{r CWT Sep24}
# take residuals
GPP_SR_Sep24_res1 <- daily_q10(GPP_SR_Sep24, "SR", "Rh", "Ra")
write.csv(GPP_SR_Sep24_res1, paste0(dir_res1_df, "Sep24.csv"), row.names = F)

# residual Rh
wc_rRh_Sep24 <- wc_summary(GPP_SR_Sep24_res1, "rRh")

# heatmap
wc_img_gen(wc_rRh_Sep24, "rRh")

# temporal power data & graph
rRh_GPP_Sep24_pwr <- wc_avg(wc_rRh_Sep24$GPP, 25)
rRh_PAR_Sep24_pwr <- wc_avg(wc_rRh_Sep24$PAR, 25)
rRh_Ts_Sep24_pwr <- wc_avg(wc_rRh_Sep24$Ts, 25)
rRh_VWC_Sep24_pwr <- wc_avg(wc_rRh_Sep24$VWC, 25)

# csv output
write.csv(rRh_GPP_Sep24_pwr$df, paste0(dir_res1_pwr, "rRh_GPP_Sep24.csv"), row.names = F)
write.csv(rRh_PAR_Sep24_pwr$df, paste0(dir_res1_pwr, "rRh_PAR_Sep24.csv"), row.names = F)
write.csv(rRh_Ts_Sep24_pwr$df, paste0(dir_res1_pwr, "rRh_Ts_Sep24.csv"), row.names = F)
write.csv(rRh_VWC_Sep24_pwr$df, paste0(dir_res1_pwr, "rRh_VWC_Sep24.csv"), row.names = F)

# extracting diurnal angle & power patterns from heatmap
wc_rRh_Sep24_diurnal_summary <- wc_result_summary(GPP_SR_Sep24_res1, "rRh", wc_rRh_Sep24)
save_to_csv(wc_rRh_Sep24_diurnal_summary, dir_res1_diurnal, "wc_rRh_Sep24_")

# viz
ggarrange(
  wc_lag_img(wc_rRh_Sep24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRh_Sep24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Sep24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Sep24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)


# residual Ra
wc_rRa_Sep24 <- wc_summary(GPP_SR_Sep24_res1, "rRa")

# heatmap
wc_img_gen(wc_rRa_Sep24, "rRa")

# temporal power data & graph
rRa_GPP_Sep24_pwr <- wc_avg(wc_rRa_Sep24$GPP, 25)
rRa_PAR_Sep24_pwr <- wc_avg(wc_rRa_Sep24$PAR, 25)
rRa_Ts_Sep24_pwr <- wc_avg(wc_rRa_Sep24$Ts, 25)
rRa_VWC_Sep24_pwr <- wc_avg(wc_rRa_Sep24$VWC, 25)

# csv output
write.csv(rRa_GPP_Sep24_pwr$df, paste0(dir_res1_pwr, "rRa_GPP_Sep24.csv"), row.names = F)
write.csv(rRa_PAR_Sep24_pwr$df, paste0(dir_res1_pwr, "rRa_PAR_Sep24.csv"), row.names = F)
write.csv(rRa_Ts_Sep24_pwr$df, paste0(dir_res1_pwr, "rRa_Ts_Sep24.csv"), row.names = F)
write.csv(rRa_VWC_Sep24_pwr$df, paste0(dir_res1_pwr, "rRa_VWC_Sep24.csv"), row.names = F)


# extracting diurnal angle & power patterns from heatmap
wc_rRa_Sep24_diurnal_summary <- wc_result_summary(GPP_SR_Sep24_res1, "rRa", wc_rRa_Sep24)
save_to_csv(wc_rRa_Sep24_diurnal_summary, dir_res1_diurnal, "wc_rRa_Sep24_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_Sep24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRa_Sep24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Sep24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Sep24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)
```

```{r WT Sep24}
wt_rRh_Sep24 <- 
  analyze.wavelet(wc_rRh_Sep24$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_Sep24_pwr <- wt_avg(wt_rRh_Sep24, 25)
write.csv(rRh_Sep24_pwr$df, paste0(dir_res1_pwr, "rRh_Sep24.csv"), row.names = F)

wt.image(wt_rRh_Sep24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRh"
)

# rRa
wt_rRa_Sep24 <- 
  analyze.wavelet(wc_rRa_Sep24$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_Sep24_pwr <- wt_avg(wt_rRa_Sep24, 25)
write.csv(rRa_Sep24_pwr$df, paste0(dir_res1_pwr, "rRa_Sep24.csv"), row.names = F)

wt.image(wt_rRa_Sep24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRa"
)
```

```{r CWT Oct24}
# take residuals
GPP_SR_Oct24_res1 <- daily_q10(GPP_SR_Oct24, "SR", "Rh", "Ra")
write.csv(GPP_SR_Oct24_res1, paste0(dir_res1_df, "Oct24.csv"), row.names = F)

# residual Rh
wc_rRh_Oct24 <- wc_summary(GPP_SR_Oct24_res1, "rRh")

# heatmap
wc_img_gen(wc_rRh_Oct24, "rRh")

# temporal power data & graph
rRh_GPP_Oct24_pwr <- wc_avg(wc_rRh_Oct24$GPP, 25)
rRh_PAR_Oct24_pwr <- wc_avg(wc_rRh_Oct24$PAR, 25)
rRh_Ts_Oct24_pwr <- wc_avg(wc_rRh_Oct24$Ts, 25)
rRh_VWC_Oct24_pwr <- wc_avg(wc_rRh_Oct24$VWC, 25)

# csv output
write.csv(rRh_GPP_Oct24_pwr$df, paste0(dir_res1_pwr, "rRh_GPP_Oct24.csv"), row.names = F)
write.csv(rRh_PAR_Oct24_pwr$df, paste0(dir_res1_pwr, "rRh_PAR_Oct24.csv"), row.names = F)
write.csv(rRh_Ts_Oct24_pwr$df, paste0(dir_res1_pwr, "rRh_Ts_Oct24.csv"), row.names = F)
write.csv(rRh_VWC_Oct24_pwr$df, paste0(dir_res1_pwr, "rRh_VWC_Oct24.csv"), row.names = F)

# extracting diurnal angle & power patterns from heatmap
wc_rRh_Oct24_diurnal_summary <- wc_result_summary(GPP_SR_Oct24_res1, "rRh", wc_rRh_Oct24)
save_to_csv(wc_rRh_Oct24_diurnal_summary, dir_res1_diurnal, "wc_rRh_Oct24_")

# viz
ggarrange(
  wc_lag_img(wc_rRh_Oct24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRh_Oct24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Oct24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Oct24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)


# residual Ra
wc_rRa_Oct24 <- wc_summary(GPP_SR_Oct24_res1, "rRa")

# heatmap
wc_img_gen(wc_rRa_Oct24, "rRa")

# temporal power data & graph
rRa_GPP_Oct24_pwr <- wc_avg(wc_rRa_Oct24$GPP, 25)
rRa_PAR_Oct24_pwr <- wc_avg(wc_rRa_Oct24$PAR, 25)
rRa_Ts_Oct24_pwr <- wc_avg(wc_rRa_Oct24$Ts, 25)
rRa_VWC_Oct24_pwr <- wc_avg(wc_rRa_Oct24$VWC, 25)

# csv output
write.csv(rRa_GPP_Oct24_pwr$df, paste0(dir_res1_pwr, "rRa_GPP_Oct24.csv"), row.names = F)
write.csv(rRa_PAR_Oct24_pwr$df, paste0(dir_res1_pwr, "rRa_PAR_Oct24.csv"), row.names = F)
write.csv(rRa_Ts_Oct24_pwr$df, paste0(dir_res1_pwr, "rRa_Ts_Oct24.csv"), row.names = F)
write.csv(rRa_VWC_Oct24_pwr$df, paste0(dir_res1_pwr, "rRa_VWC_Oct24.csv"), row.names = F)


# extracting diurnal angle & power patterns from heatmap
wc_rRa_Oct24_diurnal_summary <- wc_result_summary(GPP_SR_Oct24_res1, "rRa", wc_rRa_Oct24)
save_to_csv(wc_rRa_Oct24_diurnal_summary, dir_res1_diurnal, "wc_rRa_Oct24_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_Oct24_diurnal_summary$GPP, "GPP"),
  wc_lag_img(wc_rRa_Oct24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Oct24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Oct24_diurnal_summary$VWC, "VWC"),
  ncol = 2, nrow = 2, common.legend = T
)
```

```{r WT Oct24}
wt_rRh_Oct24 <- 
  analyze.wavelet(wc_rRh_Oct24$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_Oct24_pwr <- wt_avg(wt_rRh_Oct24, 25)
write.csv(rRh_Oct24_pwr$df, paste0(dir_res1_pwr, "rRh_Oct24.csv"), row.names = F)

wt.image(wt_rRh_Oct24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRh"
)

# rRa
wt_rRa_Oct24 <- 
  analyze.wavelet(wc_rRa_Oct24$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_Oct24_pwr <- wt_avg(wt_rRa_Oct24, 25)
write.csv(rRa_Oct24_pwr$df, paste0(dir_res1_pwr, "rRa_Oct24.csv"), row.names = F)

wt.image(wt_rRa_Oct24,  
         legend.params = 
             list(
                 lab = "wavelet power levels", # axis label
                 lab.line = 1.5, # distance between bar label and axis label
                 mar = 5
             ), 
         lvl = 0.3,
         timelab = "",
         show.date = T, 
         date.format = "%Y-%m-%d %H:%M:%S",
         periodlab = "period (days)",
         main = "rRa"
)
```
