---
title: "wavelet angle test"
author: "Moeka"
date: "2024-07-04"
output: github_document
---
wavelet analysis: chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/http://www.hs-stat.com/projects/WaveletComp/WaveletComp_guided_tour.pdf

- would it be better after deciding the period when thinking about the range??
- Normalization
All time series should be normalized to have zero mean and unit variance prior to wavelet analysis.  

- Gaps
Missing values in all the variables should be padded with zeros.

- results files are at DC_auto > Data > result_pad_64d_res

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(WaveletComp)
library(lubridate)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(tidyr)
library(broom)
library(forestmangr)
library(gridExtra)
library(mice)
library(purrr)
library(FluxGapsR)
library(missRanger)
```


```{r read a df}
setwd("G:/My Drive/Research/Projects/DC_auto/Data")

# read the dataframe - check the CRK_cont_SR_qaqc.Rmd for the quqa steps
SR_tower <- 
  read.csv("CRK_SR_tower_combined.csv", header = T) %>%
  mutate(Datetime_hr_CST = as_datetime(Datetime_hr_CST, tz = "Etc/GMT+6"))

```

- SR & Rh to use
- Spring 22 (M1-2): 2022-05-22 11:00:00 ~ 2022-06-09 15:00:00
- Winter 23 (M11): 2023-03-15 20:00:00 ~ 2023-04-05 19:00:00
- Spring 23 (M0-1): 2023-05-01 01:00:00 ~ 2023-06-06 14:00:00
- Winter 24 (M3): 2024-01-24 ~ 2024-02-05
- Winter 24-2 (M4-5): 2024-02-20 ~ 2024-03-20
- Spring 24 (M5-6):  2024-03-21 ~ 2024-04-27

- Don't use either due to too short or bad quality
- Winter 22 (M7): 2022-11-23 ~ 2022-11-30 (1 week)
 

- Only SR
- Spr22: End of Apr - 2022-05-22 10:00:00
- Fall22: Mid Aug - Beginning of Oct 
* 1 week gap in the end of August
- Grow23: 2023-03-10 ~ 2023-08-27 20:00:00 




```{r Extract the period of study}

extract_period <- function(START, END){
  df <-
    SR_tower %>%
    filter(Datetime_hr_CST >= START & Datetime_hr_CST <= END) %>%
    rename(date = Datetime_hr_CST) # let wc analysis recognize the date column
  return(df)
}


### For SR and Rh ###
# 2022

SR_Rh_May22 <- extract_period("2022-05-22 12:00:00", "2022-06-09 16:00:00")
# SR_Rh_Wnt22 <- extract_period("2022-11-23 13:00:00", "2022-11-30 16:00:00") # only a week

# 2023
# Winter 23 (M11): 2023-03-15 20:00:00 ~ 2023-04-05 19:00:00
SR_Rh_Mar23 <- extract_period("2023-03-15 21:00:00", "2023-04-05 20:00:00") 
# SR_Rh_Spr23 <- extract_period("2023-03-15 21:00:00", "2023-03-31 14:00:00") # Rh missing periodically
# SR_Rh_Spr23_2 <- extract_period("2023-05-01 01:00:00", "2023-05-15 15:00:00")
# SR_Rh_Spr23_3 <- extract_period("2023-05-23 18:00:00", "2023-06-06 14:00:00") # Rh missing periodically

# too much gaps
# 2023-05-08 23:00:00 ~ 2023-05-11 16:00:00
# 2023-05-23 17:00:00 ~ 2023-05-25 15:00:00

#SR_Rh_Spr23 <- extract_period("2023-05-01 01:00:00", "2023-06-06 14:00:00")

# 2024
SR_Rh_Jan24 <- extract_period("2024-01-25 09:00:00", "2024-02-04 12:00:00")

SR_Rh_Feb24 <- 
  extract_period("2024-02-20 14:00:00", "2024-03-20 23:59:00") %>% 
  rowwise() %>%
  mutate(SR = mean(c(SR1, SR2), na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Ra = SR - Rh)


SR_Rh_Mar24 <- 
  extract_period("2024-03-21 00:00:00", "2024-04-27 13:00:00") %>% 
  rowwise() %>%
  mutate(SR = mean(c(SR1, SR2), na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(Ra = SR - Rh)

### For SR ###
# SR_grow23 <- 
#   SR_tower %>%
#   filter(Datetime_hr_CST > "2023-03-10" & Datetime_hr_CST < "2023-8-27 20:00:00") 
```

```{r Prep before the wavelet analysis}
# normalize with 0 mean and unit variance - use scale()

# for cross wavelet analysis with Morlet function (continuous) 
scale_pad <- function(df, var1, var2){
  df %>%
    select(date, var1, var2) %>%
    mutate(NA_flag = ifelse(!is.na(df[[var1]]) & !is.na(df[[var2]]), "0", "1")) %>%
    mutate(across(where(is.numeric), scale)) %>%
    mutate(across(where(is.numeric), ~replace(., is.na(.), 0)))
}

# function to calculate daily q10 and base respiration at 20 C
daily_q10 <- function(df, SR_col, Rh_col, Ra_col){
  
  df1 <- df %>%
    mutate(day = lubridate::date(date)) %>%
    rename("SR" = !!sym(SR_col)) %>%
    rename("Rh" = !!sym(Rh_col)) %>%
    rename("Ra" = !!sym(Ra_col)) 

  
  # for SR
  df_SR <- 
    df1 %>%
    nls_table(
      SR ~ R20 * Q10^((TS_1_1_1 - 20) / (10)),
      mod_start = c(R20 = 4, Q10 = 2),
      .groups = "day") %>%
    as.data.frame() %>%
    rename("SR20" = "b0", "Q10_SR" = "b1")
  
  df_Rh <- 
    df1 %>%
    nls_table(
      Rh ~ R20 * Q10^((TS_1_1_1 - 20) / (10)),
      mod_start = c(R20 = 4, Q10 = 2),
      .groups = "day") %>%
    as.data.frame() %>%
    rename("Rh20" = "b0", "Q10_Rh" = "b1")
  
  df_Ra <- 
    df1 %>%
    nls_table(
      Ra ~ R20 * Q10^((TS_1_1_1 - 20) / (10)),
      mod_start = c(R20 = 4, Q10 = 2),
      .groups = "day") %>%
    as.data.frame() %>%
    rename("Ra20" = "b0", "Q10_Ra" = "b1")
    
  
  df2 <- 
    list(df_SR, df_Rh, df_Ra) %>% 
    reduce(full_join, by = 'day') 
  
  output <- 
    left_join(df1, df2, by = "day") %>%
    mutate(
      mSR = SR20 * Q10_SR ^ ((TS_1_1_1 - 20) / (10)),
      mRh = Rh20 * Q10_Rh ^ ((TS_1_1_1 - 20) / (10)),
      mRa = Ra20 * Q10_Ra ^ ((TS_1_1_1 - 20) / (10))
           ) %>% 
    mutate(
      rSR = SR - mSR,
      rRh = Rh - mRh,
      rRa = Ra - mRa
    )
    
  
  return(output)
}

# function to check the amount (%) of the gaps
pMiss <- function(x){
  sum(is.na(x)) / length(x) * 100
  }


# Detect gap lengths in the time series
detect_gaps <- function(data, col) {
  
  mt <- is.na(data[, col])
  ind <- 1 # index for marking the gaps
  mk <- vector()
  
  for (i in 1:length(mt)) {
    if (mt[i] == FALSE) {
      mk[i] <- 0 # non-gaps are marked as 0
    } else {
      if (mt[i] == TRUE) {
        mk[i] <- ind # gaps are marked as the value of ind
        if (i != length(mt)){ # to prevent the error when loop reach the end
          if (mt[i + 1] == FALSE) {
            ind <- ind + 1 # when reached the end of a gap, change add 1 to ind
          }
        }
      }
    }
  }
  
  stat <- table(mk)[-1] # number of data points in each gap
  # print using "cat" for break into lines
  cat(paste0("","\n",
             "##### Summary #####","\n",
             "","\n",
             "Total gaps:       ",max(mk),"\n",
             "< 6 hrs:          ",sum(stat < 6),"\n",
             ">= 6 hrs < 1 day: ",sum(stat >= 6 & stat < 24),"\n",
             ">= 1 & < 2 days:  ",sum(stat >= 24 & stat < 24*2),"\n",
             ">= 2 days:        ",sum(stat >= 24*2)
  ))
}


# function to write a list of dfs to csvs
save_to_csv <- function(list_of_dfs, dir, fname){
  for (i in seq_along(list_of_dfs)) {
  write.csv(list_of_dfs[[i]], paste0(dir, fname, names(list_of_dfs)[i], ".csv"), row.names = FALSE)
  }
}

```


```{r cross wavelet - continuous}

coh <- function(df, var1, var2, upper){
  df1 <- scale_pad(df, var1, var2)
  analyze.coherency(df1, my.pair = c(var1, var2),
                          loess.span = 0,     ## no detrending required
                          dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                          dj = 1/100,         ## resolution along period axis
                          lowerPeriod = 1/4,  ## 6 hour
                          upperPeriod = upper,
                          make.pval = T,      ## check for significance
                          n.sim = 10)         ## 10 white-noise simulations used for assessing significance 
}

# function to generate a cross-wavelet power spectrum
wc_img <- 
  function(df, title){
  
  dev.new(width = 6, height = 5, noRStudioGD = TRUE)
  
  wc.image(
    df,
    legend.params = 
      list(
        lab = "cross-wavelet power levels", # axis label
        lab.line = 1.5, # distance between bar label and axis label
        mar = 5
        ), 
    lvl = 0.3,
    timelab = "",
    show.date = T, 
    date.format = "%Y-%m-%d %H:%M:%S",
    periodlab = "period (days)",
    main = title
    )

}

# function to analyze and plot them all not recommended for a longer period  of
# term

# does not work well when assign an object name..
# want to make a timestamp x axis - too crowded w/ hourly timestamps
wc_summary <- function(df, resp_var){
  
  wc_results <- list()
  
  # wc result
  wc_results[["PAR"]] <- coh(df, resp_var, "PPFD_IN_1_1_1", 64)
  wc_results[["Ts"]] <- coh(df, resp_var,"TS_1_1_1", 64)
  wc_results[["SWC"]] <- coh(df, resp_var, "SWC_1_1_1", 64)

  return(wc_results)
  }

# this will generate all 4 plots one by one
wc_img_gen <- function(df, resp_var){
 # par(mar=c(2,2,1.5,0.3)+0.1)
  par(plt = c(0.1, 0.95, 0.1, 0.95))
  wc_img(df[["PAR"]], paste0(resp_var, " vs PAR"))
  wc_img(df[["Ts"]], paste0(resp_var, " vs Ts"))
  wc_img(df[["SWC"]], paste0(resp_var, " vs SWC"))

}

# this will generate all 4 plots one by one
wc_avg_gen <- function(df, resp_var){

  wc.avg(df[["PAR"]], main = paste0(resp_var, " vs PAR"), siglvl = 0.05, sigcol = "black", 
         sigpch = 20, periodlab = "", show.legend = F, averagelab = "", maximum.level = 25)
  
  wc.avg(df[["Ts"]], main = paste0(resp_var, " vs Ts"), siglvl = 0.05, sigcol = "black", 
         sigpch = 20, periodlab = "", show.legend = F, averagelab = "", maximum.level = 25)
  
  wc.avg(df[["SWC"]], main = paste0(resp_var, " vs SWC"), siglvl = 0.05, sigcol = "black", 
         sigpch = 20, periodlab = "", show.legend = F, averagelab = "", maximum.level = 25)
  
}

# function to generate result df
coh_result <- function(pad_df, coh_df){
  
  # extracting the p-value at Period 1
  result <- 
    cbind(pad_df, data.frame(pval_period1 = coh_df$Power.xy.pval[201,])) 
  
  # Average angles between Period 0.5 - 1.5
  # ASSUMING THE Y_AXIS IS LOG-BASED
  result$Angle_raw <- colMeans(data.frame(coh_df$Angle[101:211,])) 
  result$Power_raw <- colMeans(data.frame(coh_df$Power.xy[101:211,])) 
  
  # Result df with NA_flag, and running averages
  result <- 
    result %>%
    mutate(Angle = ifelse(NA_flag == "0" & pval_period1 < 0.1, Angle_raw, NA),
           Angle_1d = zoo::rollmean(Angle, k = 24, fill = NA),      # 1 day moving avg - 24
           Angle_7d = zoo::rollmean(Angle, k = 24*7, fill = NA),    # 7 days moving avg - 24*7
           Angle_15d = zoo::rollmean(Angle, k = 24*15, fill = NA),  # 15 days moving avg - 24*15
           Power = ifelse(NA_flag == "0" & pval_period1 < 0.1, Power_raw, NA),
           Power_1d = zoo::rollmean(Power, k = 24, fill = NA),      # 1 day moving avg - 24
           Power_7d = zoo::rollmean(Power, k = 24*7, fill = NA),    # 7 days moving avg - 24*7
           Power_15d = zoo::rollmean(Power, k = 24*15, fill = NA))  # 15 days moving avg - 24*15
  return(result)
}

# FOR VIZ
wc_lag_img <- function(result_df, title){
  
  result_df$date <- as_datetime(result_df$date)
  
  # 1: the midtime to have a time (00:00)
  # 2: if / included use mdy_hm, not use ymd_hms
  # result_df$date <- ifelse(grepl("/", result_df$date), 
  #                          as_datetime(ifelse(grepl(":",date), as.POSIXct(date, format = '%m/%d/%Y %H:%M'),
  #                                          as.POSIXct(date, format = '%m/%d/%Y'))),
  #                          as_datetime(date) 
  #                          )
  
  pivot_longer(result_df, 
               cols = c(Angle, Angle_1d, Angle_7d, Angle_15d),
               names_to = "Variable", 
               values_to = "Value"
               ) %>%
    ggplot() +
    geom_point(aes(date, 24 * Value / (2 * pi), col = Variable)) +
    scale_color_manual(breaks=c("Angle", "Angle_1d", "Angle_7d", "Angle_15d"),
                       values = c("#A0B1BA", "#045275", "#089099", "#7CCBA2")) + 
    theme_classic() + ylab("Hours") + 
    ggtitle(title) +
    geom_abline(slope = 0, intercept = 0) + 
    theme(
      legend.position="top",
      axis.title.x = element_blank(),axis.text.x = element_text(size = 20),
      axis.title.y = element_text(size = 20), axis.text.y = element_text(size = 20),
      legend.title = element_blank(), legend.text = element_text(size = 20),
      axis.ticks.x=element_blank()
      ) +
    scale_x_datetime(date_breaks = "2 week", date_labels = "%B %d") 
}



# summarize the result 
wc_result_summary <- function(orig_df, resp_var, wc_sum_df){
  
  scale_pad_summary <- list()
  
  scale_pad_summary[["PAR"]] <- scale_pad(orig_df, resp_var, "PPFD_IN_1_1_1")
  scale_pad_summary[["Ts"]] <- scale_pad(orig_df, resp_var, "TS_1_1_1")
  scale_pad_summary[["SWC"]] <- scale_pad(orig_df, resp_var, "SWC_1_1_1")
  
  results <- list()
  
  results[["PAR"]] <- coh_result(scale_pad_summary[["PAR"]], wc_sum_df$PAR)
  results[["Ts"]] <- coh_result(scale_pad_summary[["Ts"]], wc_sum_df$Ts)
  results[["SWC"]] <- coh_result(scale_pad_summary[["SWC"]], wc_sum_df$SWC)
  
  return(results)
}

                                              

```

```{r temporal pwr df & ggplot}
wt_avg <- function(df, ymax){
    
    if (class(df) != "analyze.wavelet") {
        stop("Your object class is not 'analyze.wavelet'")
    }
    
    # Create the dataframe
    output_df <- 
        data.frame(
            Period = df[["Period"]], 
            Power.avg = df[["Power.avg"]],
            Power.avg.pval = df[["Power.avg.pval"]]
        ) %>%
        mutate(Power.avg.sig = ifelse(Power.avg.pval < 0.05, Power.avg, NA))
    
    # Create the plot
    p1 <- 
        ggplot(output_df) + 
        geom_line(aes(log2(Period), Power.avg)) +
        geom_point(aes(log2(Period), Power.avg.sig), size = 3) + 
        theme_classic() + 
        ylab("Avg. Wavelet Spectram") + 
        xlab("Period (days; log scale)") +
        scale_x_continuous(
            breaks = c(0, 3, 6),
            label = c(1, 8, 64)
        ) +
        scale_y_continuous(
            breaks = c(0, 10, 20),
            limits = c(0, ymax)
        ) +
        theme(
            axis.title.x = element_text(size = 25), 
            axis.text.x = element_text(size = 25),
            axis.title.y = element_text(size = 25), 
            axis.text.y = element_text(size = 25),
            legend.title = element_text(size = 25), 
            legend.text = element_text(size = 25),
            panel.border = element_rect(colour = "black", fill = NA, linewidth = 1)
        )
    
    # Return both the dataframe and plot as a list
    return(list(df = output_df, plot = p1))
}


wc_avg <- function(df, ymax){
  
    if (class(df) == "analyze.wavelet") {
      stop("Your object class is 'analyze.wavelet' - use wt_img_gg")
    }
  
   # Create the dataframe
    output_df <- 
        data.frame(
            Period = df[["Period"]], 
            Power.avg = df[["Power.xy.avg"]],
            Power.avg.pval = df[["Power.xy.avg.pval"]]
        ) %>%
        mutate(Power.avg.sig = ifelse(Power.avg.pval < 0.05, Power.avg, NA))
      
      
      p1 <- 
        ggplot() + 
        geom_line(aes(log2(Period), Power.avg)) +
        geom_point(aes(log2(Period), Power.avg.sig), size = 3) + 
        theme_classic() + 
        ylab("Avg. Wavelet Spectram") + xlab("Period (days; log scale)") +
        scale_x_continuous(
          breaks = c(0, 3, 6),
          label = c(1, 8, 64)
          ) +
        scale_y_continuous(
          breaks = c(0, 10, 20),
          limits = c(0, ymax)
          ) + 
        theme(
          axis.title.x = element_text(size = 25), 
          axis.text.x = element_text(size = 25),
          axis.title.y = element_text(size = 25), 
          axis.text.y = element_text(size = 25),
          legend.title = element_text(size = 25), 
          legend.text = element_text(size = 25),
          panel.border = element_rect(colour = "black", fill = NA, linewidth = 1)
          ) 

    # Return both the dataframe and plot as a list
    return(list(df = output_df, plot = p1))
  
}


```

```{r location to save}
dir_pwr = "G:/My Drive/Research/Projects/DC_auto/Data/Nov2024_rerun/Re_result_pad_64d_res/df_temporal_pwr/"
dir_diurnal = "G:/My Drive/Research/Projects/DC_auto/Data/Nov2024_rerun/Re_result_pad_64d_res/df_diurnal/"

```

```{r CWT 2022}
apply(SR_Rh_May22, 2, pMiss)

# gap length 
# only PAR
detect_gaps(SR_Rh_May22, "PPFD_IN_1_1_1")

# take residuals
SR_Rh_May22_res <- daily_q10(SR_Rh_May22, "SR1", "Rh", "Ra1")
write.csv(SR_Rh_May22_res, "G:/My Drive/Research/Projects/DC_auto/Data/Nov2024_rerun/Re_result_pad_64d_res/df/C1.csv", row.names = F)

# residual Rh
wc_rRh_May22 <- wc_summary(SR_Rh_May22_res, "rRh")

# heatmap
wc_img_gen(wc_rRh_May22, "rRh")

# temporal power data & graph
rRh_PAR_May22_pwr <- wc_avg(wc_rRh_May22$PAR, 25)
rRh_Ts_May22_pwr <- wc_avg(wc_rRh_May22$Ts, 25)
rRh_SWC_May22_pwr <- wc_avg(wc_rRh_May22$SWC, 25)

# csv output
write.csv(rRh_PAR_May22_pwr$df, paste0(dir_pwr, "C1_rRh_PAR_May22.csv"), row.names = F)
write.csv(rRh_Ts_May22_pwr$df, paste0(dir_pwr, "C1_rRh_Ts_May22.csv"), row.names = F)
write.csv(rRh_SWC_May22_pwr$df, paste0(dir_pwr, "C1_rRh_SWC_May22.csv"), row.names = F)

# extracting diurnal angle & power patterns from heatmap
wc_rRh_May22_diurnal_summary <- wc_result_summary(SR_Rh_May22_res, "rRh", wc_rRh_May22)
save_to_csv(wc_rRh_May22_diurnal_summary, dir_diurnal, "C1_wc_rRh_May22_")


# viz
ggarrange(
  wc_lag_img(wc_rRh_May22_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_May22_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_May22_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
)


# residual Ra
wc_rRa_May22 <- wc_summary(SR_Rh_May22_res, "rRa")
wc_img_gen(wc_rRa_May22, "rRa")

# temporal power data & graph
rRa_PAR_May22_pwr <- wc_avg(wc_rRa_May22$PAR, 25)
rRa_Ts_May22_pwr <- wc_avg(wc_rRa_May22$Ts, 25)
rRa_SWC_May22_pwr <- wc_avg(wc_rRa_May22$SWC, 25)

# csv output
write.csv(rRa_PAR_May22_pwr$df, paste0(dir_pwr, "C1_rRa_PAR_May22.csv"), row.names = F)
write.csv(rRa_Ts_May22_pwr$df, paste0(dir_pwr, "C1_rRa_Ts_May22.csv"), row.names = F)
write.csv(rRa_SWC_May22_pwr$df, paste0(dir_pwr, "C1_rRa_SWC_May22.csv"), row.names = F)

# extracting diurnal angle & power patterns from heatmap
wc_rRa_May22_diurnal_summary <- wc_result_summary(SR_Rh_May22_res, "rRa", wc_rRa_May22)
save_to_csv(wc_rRa_May22_diurnal_summary, dir_diurnal, "C1_wc_rRa_May22_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_May22_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_May22_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_May22_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
)

```

```{r WT 2022}
wt_rRh_May22 <- 
  analyze.wavelet(wc_rRh_May22$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_May22_pwr <- wt_avg(wt_rRh_May22, 25)
write.csv(rRh_May22_pwr$df, paste0(dir_pwr, "C1_rRh_May22.csv"), row.names = F)

# rRa
wt_rRa_May22 <- 
  analyze.wavelet(wc_rRa_May22$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_May22_pwr <- wt_avg(wt_rRa_May22, 25)
write.csv(rRa_May22_pwr$df, paste0(dir_pwr, "C1_rRa_May22.csv"), row.names = F)
```


```{r CWT Mar23}
apply(SR_Rh_Mar23, 2, pMiss)

# gap length 
detect_gaps(SR_Rh_Mar23, "TS_1_1_1")
detect_gaps(SR_Rh_Mar23, "SWC_1_1_1")
detect_gaps(SR_Rh_Mar23, "SR1")
detect_gaps(SR_Rh_Mar23, "Rh")
detect_gaps(SR_Rh_Mar23, "Ra1")

SR_Rh_Mar23_res <-
  daily_q10(SR_Rh_Mar23, "SR1", "Rh", "Ra1")
write.csv(SR_Rh_Mar23_res, "G:/My Drive/Research/Projects/DC_auto/Data/Nov2024_rerun/Re_result_pad_64d_res/df/C2.csv", row.names = F)

# residual Rh
wc_rRh_Mar23 <- wc_summary(SR_Rh_Mar23_res, "rRh")
wc_img_gen(wc_rRh_Mar23, "rRh")

# temporal power data & graph
rRh_PAR_Mar23_pwr <- wc_avg(wc_rRh_Mar23$PAR, 25)
rRh_Ts_Mar23_pwr <- wc_avg(wc_rRh_Mar23$Ts, 25)
rRh_SWC_Mar23_pwr <- wc_avg(wc_rRh_Mar23$SWC, 25)

# csv output
write.csv(rRh_PAR_Mar23_pwr$df, paste0(dir_pwr, "C2_rRh_PAR_Mar23.csv"), row.names = F)
write.csv(rRh_Ts_Mar23_pwr$df, paste0(dir_pwr, "C2_rRh_Ts_Mar23.csv"), row.names = F)
write.csv(rRh_SWC_Mar23_pwr$df, paste0(dir_pwr, "C2_rRh_SWC_Mar23.csv"), row.names = F)

# result
wc_rRh_Mar23_diurnal_summary <- wc_result_summary(SR_Rh_Mar23_res, "rRh", wc_rRh_Mar23)
save_to_csv(wc_rRh_Mar23_diurnal_summary, dir_diurnal, "C2_wc_rRh_Mar23_")

# viz
ggarrange(
  wc_lag_img(wc_rRh_Mar23_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Mar23_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Mar23_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
)


# residual Ra
wc_rRa_Mar23 <- wc_summary(SR_Rh_Mar23_res, "rRa")
wc_img_gen(wc_rRa_Mar23, "rRa")

# temporal power data & graph
rRa_PAR_Mar23_pwr <- wc_avg(wc_rRa_Mar23$PAR, 25)
rRa_Ts_Mar23_pwr <- wc_avg(wc_rRa_Mar23$Ts, 25)
rRa_SWC_Mar23_pwr <- wc_avg(wc_rRa_Mar23$SWC, 25)

# csv output
write.csv(rRa_PAR_Mar23_pwr$df, paste0(dir_pwr, "C2_rRa_PAR_Mar23.csv"), row.names = F)
write.csv(rRa_Ts_Mar23_pwr$df, paste0(dir_pwr, "C2_rRa_Ts_Mar23.csv"), row.names = F)
write.csv(rRa_SWC_Mar23_pwr$df, paste0(dir_pwr, "C2_rRa_SWC_Mar23.csv"), row.names = F)

# summary
wc_rRa_Mar23_diurnal_summary <- wc_result_summary(SR_Rh_Mar23_res, "Ra", wc_rRa_Mar23)
save_to_csv(wc_rRa_Mar23_diurnal_summary, dir_diurnal, "C2_wc_rRa_Mar23_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_Mar23_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Mar23_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Mar23_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
  )  

```

```{r WT Mar23}
wt_rRh_Mar23 <- 
  analyze.wavelet(wc_rRh_Mar23$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )


rRh_Mar23_pwr <- wt_avg(wt_rRh_Mar23, 25)
write.csv(rRh_Mar23_pwr$df, paste0(dir_pwr, "C2_rRh_Mar23.csv"), row.names = F)

# rRa
wt_rRa_Mar23 <- 
  analyze.wavelet(wc_rRa_Mar23$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_Mar23_pwr <- wt_avg(wt_rRa_Mar23, 25)
write.csv(rRa_Mar23_pwr$df, paste0(dir_pwr, "C2_rRa_Mar23.csv"), row.names = F)
```



```{r CWT 24}

apply(SR_Rh_Jan24, 2, pMiss)

# gap length 
# only SR1, Rh, Ra1
detect_gaps(SR_Rh_Jan24, "SR1")
detect_gaps(SR_Rh_Jan24, "Rh")
detect_gaps(SR_Rh_Jan24, "Ra1")

SR_Rh_Jan24_res <- daily_q10(SR_Rh_Jan24, "SR1", "Rh", "Ra1")
write.csv(SR_Rh_Jan24_res, "G:/My Drive/Research/Projects/DC_auto/Data/Nov2024_rerun/Re_result_pad_64d_res/df/C3.csv", row.names = F)

# Rh residual
wc_rRh_Jan24 <- wc_summary(SR_Rh_Jan24_res, "rRh")

wc_img_gen(wc_rRh_Jan24, "rRh")

# power avg
rRh_PAR_Jan24_pwr <- wc_avg(wc_rRh_Jan24$PAR, 25)
rRh_Ts_Jan24_pwr <- wc_avg(wc_rRh_Jan24$Ts, 25)
rRh_SWC_Jan24_pwr <- wc_avg(wc_rRh_Jan24$SWC, 25)

# csv output
write.csv(rRh_PAR_Jan24_pwr$df, paste0(dir_pwr, "C3_rRh_PAR_Jan24.csv"), row.names = F)
write.csv(rRh_Ts_Jan24_pwr$df, paste0(dir_pwr, "C3_rRh_Ts_Jan24.csv"), row.names = F)
write.csv(rRh_SWC_Jan24_pwr$df, paste0(dir_pwr, "C3_rRh_SWC_Jan24.csv"), row.names = F)

wc_rRh_Jan24_diurnal_summary <- wc_result_summary(SR_Rh_Jan24_res, "rRh", wc_rRh_Jan24)
save_to_csv(wc_rRh_Jan24_diurnal_summary, dir_diurnal, "C3_wc_rRh_Jan24_")


# viz
ggarrange(
  wc_lag_img(wc_rRh_Jan24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Jan24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Jan24_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
)




# Ra residual
wc_rRa_Jan24 <- wc_summary(SR_Rh_Jan24_res, "rRa")
wc_img_gen(wc_rRa_Jan24, "rRa")

# power avg
rRa_PAR_Jan24_pwr <- wc_avg(wc_rRa_Jan24$PAR, 25)
rRa_Ts_Jan24_pwr <- wc_avg(wc_rRa_Jan24$Ts, 25)
rRa_SWC_Jan24_pwr <- wc_avg(wc_rRa_Jan24$SWC, 25)

# csv output
write.csv(rRa_PAR_Jan24_pwr$df, paste0(dir_pwr, "C3_rRa_PAR_Jan24.csv"), row.names = F)
write.csv(rRa_Ts_Jan24_pwr$df, paste0(dir_pwr, "C3_rRa_Ts_Jan24.csv"), row.names = F)
write.csv(rRa_SWC_Jan24_pwr$df, paste0(dir_pwr, "C3_rRa_SWC_Jan24.csv"), row.names = F)

# result
wc_rRa_Jan24_diurnal_summary <- wc_result_summary(SR_Rh_Jan24_res, "rRa", wc_rRa_Jan24)
save_to_csv(wc_rRa_Jan24_diurnal_summary, dir_diurnal, "C3_wc_rRa_Jan24_")


# viz
ggarrange(
  wc_lag_img(wc_rRa_Jan24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Jan24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Jan24_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
)

###################
### SR_Rh_Feb24 ###
###################


apply(SR_Rh_Feb24, 2, pMiss)

# gap length 
# only SR1, Rh, Ra1
detect_gaps(SR_Rh_Feb24, "PPFD_IN_1_1_1")
detect_gaps(SR_Rh_Feb24, "SR")
detect_gaps(SR_Rh_Feb24, "Rh")
detect_gaps(SR_Rh_Feb24, "Ra")

SR_Rh_Feb24_res <- daily_q10(SR_Rh_Feb24, "SR", "Rh", "Ra")
write.csv(SR_Rh_Feb24_res, "G:/My Drive/Research/Projects/DC_auto/Data/Nov2024_rerun/Re_result_pad_64d_res/df/C4.csv", row.names = F)

# Ra residual
wc_rRh_Feb24 <- wc_summary(SR_Rh_Feb24_res, "rRh")
wc_img_gen(wc_rRh_Feb24, "rRh")

# power avg
rRh_PAR_Feb24_pwr <- wc_avg(wc_rRh_Feb24$PAR, 25)
rRh_Ts_Feb24_pwr <- wc_avg(wc_rRh_Feb24$Ts, 25)
rRh_SWC_Feb24_pwr <- wc_avg(wc_rRh_Feb24$SWC, 25)

# csv output
write.csv(rRh_PAR_Feb24_pwr$df, paste0(dir_pwr, "C4_rRh_PAR_Feb24.csv"), row.names = F)
write.csv(rRh_Ts_Feb24_pwr$df, paste0(dir_pwr, "C4_rRh_Ts_Feb24.csv"), row.names = F)
write.csv(rRh_SWC_Feb24_pwr$df, paste0(dir_pwr, "C4_rRh_SWC_Feb24.csv"), row.names = F)

wc_rRh_Feb24_diurnal_summary <- wc_result_summary(SR_Rh_Feb24_res, "rRh", wc_rRh_Feb24)
save_to_csv(wc_rRh_Feb24_diurnal_summary, dir_diurnal, "C4_wc_rRh_Feb24_")


# viz
ggarrange(
  wc_lag_img(wc_rRh_Feb24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Feb24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Feb24_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
)




# Ra residual
wc_rRa_Feb24 <- wc_summary(SR_Rh_Feb24_res, "rRa")
wc_img_gen(wc_rRa_Feb24, "rRa")

# power avg
rRa_PAR_Feb24_pwr <- wc_avg(wc_rRa_Feb24$PAR, 25)
rRa_Ts_Feb24_pwr <- wc_avg(wc_rRa_Feb24$Ts, 25)
rRa_SWC_Feb24_pwr <- wc_avg(wc_rRa_Feb24$SWC, 25)

# csv output
write.csv(rRa_PAR_Feb24_pwr$df, paste0(dir_pwr, "C4_rRa_PAR_Feb24.csv"), row.names = F)
write.csv(rRa_Ts_Feb24_pwr$df, paste0(dir_pwr, "C4_rRa_Ts_Feb24.csv"), row.names = F)
write.csv(rRa_SWC_Feb24_pwr$df, paste0(dir_pwr, "C4_rRa_SWC_Feb24.csv"), row.names = F)

wc_rRa_Feb24_diurnal_summary <- wc_result_summary(SR_Rh_Feb24_res, "rRh", wc_rRa_Feb24)
save_to_csv(wc_rRa_Feb24_diurnal_summary, dir_diurnal, "C4_wc_rRa_Feb24_")


# viz
ggarrange(
  wc_lag_img(wc_rRa_Feb24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Feb24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Feb24_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T
)

###################
### SR_Rh_Mar24 ###
###################

apply(SR_Rh_Mar24, 2, pMiss)

detect_gaps(SR_Rh_Mar24, "PPFD_IN_1_1_1")
detect_gaps(SR_Rh_Mar24, "TS_1_1_1")
detect_gaps(SR_Rh_Mar24, "SWC_1_1_1")
detect_gaps(SR_Rh_Mar24, "SR")
detect_gaps(SR_Rh_Mar24, "Rh")
detect_gaps(SR_Rh_Mar24, "Ra")

SR_Rh_Mar24_res <- daily_q10(SR_Rh_Mar24, "SR", "Rh", "Ra")
write.csv(SR_Rh_Mar24_res, "G:/My Drive/Research/Projects/DC_auto/Data/Nov2024_rerun/Re_result_pad_64d_res/df/C5.csv", row.names = F)

# residual Rh
wc_rRh_Mar24 <- wc_summary(SR_Rh_Mar24_res, "rRh")
wc_img_gen(wc_rRh_Mar24, "rRh")

# power avg
rRh_PAR_Mar24_pwr <- wc_avg(wc_rRh_Mar24$PAR, 25)
rRh_Ts_Mar24_pwr <- wc_avg(wc_rRh_Mar24$Ts, 25)
rRh_SWC_Mar24_pwr <- wc_avg(wc_rRh_Mar24$SWC, 25)

# csv output
write.csv(rRh_PAR_Mar24_pwr$df, paste0(dir_pwr, "C5_rRh_PAR_Mar24.csv"), row.names = F)
write.csv(rRh_Ts_Mar24_pwr$df, paste0(dir_pwr, "C5_rRh_Ts_Mar24.csv"), row.names = F)
write.csv(rRh_SWC_Mar24_pwr$df, paste0(dir_pwr, "C5_rRh_SWC_Mar24.csv"), row.names = F)

wc_rRh_Mar24_diurnal_summary <- wc_result_summary(SR_Rh_Mar24_res, "rRh", wc_rRh_Mar24)
save_to_csv(wc_rRh_Mar24_diurnal_summary, dir_diurnal, "C5_wc_rRh_Mar24_")

# viz
ggarrange(
  wc_lag_img(wc_rRh_Mar24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRh_Mar24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRh_Mar24_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T)



# Residual Ra
wc_rRa_Mar24 <- wc_summary(SR_Rh_Mar24_res, "rRa")
wc_img_gen(wc_rRa_Mar24, "rRa")


# power avg
rRa_PAR_Mar24_pwr <- wc_avg(wc_rRa_Mar24$PAR, 25)
rRa_Ts_Mar24_pwr <- wc_avg(wc_rRa_Mar24$Ts, 25)
rRa_SWC_Mar24_pwr <- wc_avg(wc_rRa_Mar24$SWC, 25)

# csv output
write.csv(rRa_PAR_Mar24_pwr$df, paste0(dir_pwr, "C5_rRa_PAR_Mar24.csv"), row.names = F)
write.csv(rRa_Ts_Mar24_pwr$df, paste0(dir_pwr, "C5_rRa_Ts_Mar24.csv"), row.names = F)
write.csv(rRa_SWC_Mar24_pwr$df, paste0(dir_pwr, "C5_rRa_SWC_Mar24.csv"), row.names = F)

wc_rRa_Mar24_diurnal_summary <- wc_result_summary(SR_Rh_Mar24_res, "rRh", wc_rRa_Mar24)
save_to_csv(wc_rRa_Mar24_diurnal_summary, dir_diurnal, "C5_wc_rRa_Mar24_")

# viz
ggarrange(
  wc_lag_img(wc_rRa_Mar24_diurnal_summary$PAR, "PAR"),
  wc_lag_img(wc_rRa_Mar24_diurnal_summary$Ts, "Ts"),
  wc_lag_img(wc_rRa_Mar24_diurnal_summary$SWC, "SWC"),
  ncol = 3, common.legend = T)

```

```{r WT 2024}


wt_rRh_Jan24 <- 
  analyze.wavelet(wc_rRh_Jan24$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_Jan24_pwr <- wt_avg(wt_rRh_Jan24, 25)
write.csv(rRh_Jan24_pwr$df, paste0(dir_pwr, "C3_rRh_Jan24.csv"), row.names = F)


# rRa
wt_rRa_Jan24 <- 
  analyze.wavelet(wc_rRa_Jan24$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )


rRa_Jan24_pwr <- wt_avg(wt_rRa_Jan24, 25)
write.csv(rRa_Jan24_pwr$df, paste0(dir_pwr, "C3_rRa_Jan24.csv"), row.names = F)



wt_rRh_Feb24 <- 
  analyze.wavelet(wc_rRh_Feb24$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_Feb24_pwr <- wt_avg(wt_rRh_Feb24, 25)
write.csv(rRh_Feb24_pwr$df, paste0(dir_pwr, "C4_rRh_Feb24.csv"), row.names = F)


# rRa
wt_rRa_Feb24 <- 
  analyze.wavelet(wc_rRa_Feb24$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )


rRa_Feb24_pwr <- wt_avg(wt_rRa_Feb24, 25)
write.csv(rRa_Feb24_pwr$df, paste0(dir_pwr, "C4_rRa_Feb24.csv"), row.names = F)


wt_rRh_Mar24 <- 
  analyze.wavelet(wc_rRh_Mar24$PAR$series,"rRh", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRh_Mar24_pwr <- wt_avg(wt_rRh_Mar24, 25)
write.csv(rRh_Mar24_pwr$df, paste0(dir_pwr, "C5_rRh_Mar24.csv"), row.names = F)

# rRa
wt_rRa_Mar24 <- 
  analyze.wavelet(wc_rRa_Mar24$PAR$series,"rRa", 
                  loess.span = 0,     ## no detrending required
                  dt = 1/24,          ## defines the time unit --- there are 24 slots in a day! Time unit = 1 day
                  dj = 1/100,         ## resolution along period axis
                  lowerPeriod = 1/4,  ## 6 hour
                  upperPeriod = 64,  ## 128 days
                  make.pval = T,      ## check for significance
                  n.sim = 10)         ## 10 white-noise simulations used for assessing significance )

rRa_Mar24_pwr <- wt_avg(wt_rRa_Mar24, 25)
write.csv(rRa_Mar24_pwr$df, paste0(dir_pwr, "C5_rRa_Mar24.csv"), row.names = F)

```



```{r making dfs for diurnal peaks}

filenames_res_pwr <- 
  list.files("G:/My Drive/Research/Projects/DC_auto/Data/res_test_Mar2025/Hourly_model_diel_Q10/df_temporal_pwr/", "*.csv", full.names = T)

temp_pwr_csv <- function(filename){
  
  df <- strsplit(filename, "/")[[1]][length(strsplit(filename, "/")[[1]])]
  campaign <- strsplit(df, "_")[[1]][1]
  resp <- strsplit(df, "_")[[1]][2]
  driver <- ifelse(
      is.na(strsplit(df, "_")[[1]][4]),
      NA,
      sub("\\.csv$", "", strsplit(df, "_")[[1]][3])
    )
  
    result <- 
    read.csv(filename) %>%
    summarise(
      pwr_P1 = Power.avg[Period == "1"],
      pwr_max = max(Power.avg, na.rm = TRUE),
      pwr_max_period = Period[which.max(Power.avg)]) %>% 
    mutate(
      df = df,
      campaign = campaign,
      resp = resp,
      driver = driver
    ) 
}

res_pwr <- purrr::map_dfr(filenames_res_pwr, temp_pwr_csv)

# csv
write.csv(res_pwr, "G:/My Drive/Research/Projects/DC_auto/Data/res_test_Mar2025/Hourly_model_diel_Q10/temp_pwr_res.csv", row.names = F)


```
